---
title: "HW1_632"
author: "Prashan A. Welipitiya"
date: "2/6/2020"
output: pdf_document
---

# Exercise 1

a. $\hat{y} = -1.1016 + 2.2606x$

b. The Null Hypothesis is the slope is equal to zero. The Alternative Hypothesis is that the slope is not equal to zero. 
Based on the p-value, we reject the Null Hypothesis.

c. 
```{r}
2*pt(-2.699, 49)
```

d. 
```{r}
2.2606/0.0981
```

e.
```{r}
tc = abs(qt(.05/2, 48))
b = 2.2606
se = 0.0981
b + tc*se
b - tc*se
```

Yes, the interval is not equal to zero so it does agree with the results of the hypothesis test. 

# Exercise 3

```{r}
setwd("C:/Users/Prashan.Welipitiya/Downloads")
playbill = read.csv("playbill.csv")
```
# a. 
```{r}
par(mar=c(4.5,4.5,2,2)) #adjust margins
plot(CurrentWeek ~ LastWeek, data = playbill)
lm1 = lm(data = playbill, CurrentWeek ~ LastWeek)
abline(lm1, lwd=1.5, lty=2)
```
# b. 
```{r}
confint(lm1)["LastWeek", ]
```
1 is plausible because it is in the interval. 

# c. 
```{r}

newdata = data.frame(LastWeek=400000)
predict(lm1, newdata, interval="predict", level=.95)

```
# d. 
The lower and upper confidence levels are to far apart to assume that the two weeks will be equal. 

# Exercise 4
```{r}
library(alr4)
#help(oldfaith)
```
# a. 
```{r}
lm1 <- lm(Interval ~ Duration, data = oldfaith)
summary(lm1)
```

# b. 
```{r}
par(mar=c(4.5,4.5,2,2)) #adjust margins
plot(Interval ~ Duration, data = oldfaith)
abline(lm1, lwd=1.5, lty=2)
```

# c.
```{r}
newdata = data.frame(Duration=250)
predict(lm1, newdata, interval="predict", level=.95)
```
We expect the wait to be 78.2 seconds and the interval is a range of anywhere between 66.35 and 90.05 seconds. 

# d. 
The R squared shows a strong positive linear association. 
