---
title: "HW2_632"
author: "Prashan A. Welipitiya"
date: "2/14/2020"
output: pdf_document
---
# Exercise 1
a. Linearity, Independence, Normality, and Equal Variance. We check if the residuals vs fitted values has constant variance. We can also check if the relationship between x and y is linear.
b. Outliers are points that dont follow the bulk of the data. In SLR we identify if the interval is outside -2 to 2 or -4 to 4. 
c. Leverage points are points with an x-value that are distant from other x values. In SLR we calculate it using $h_i$ > 4/n.
d. 
error - $e_i$ ~ $N(0, \sigma^2)$
residual - $\hat{e}_i = y_i - \hat{y}_i$ 
standardized residual - $r_i = \frac{\hat{e}_i}{\hat{\sigma}\sqrt{1-h_i}}$
$Var(e_i) = \sigma^2$
$Var(\hat{e}_i) = \sigma^2[1-h_i]$

The residuals vs fitted values clearly shows if there is any unequal variance in the residuals. Also if there are no obvious patterns, then  assumptions are reasonably satisfied. 

# Exercise 2
a. False, just constant variance. 
b. True 
c. False, transforming one variable works just fine. 
d. True
e. True

# Exercise 3
```{r}
UN11 <- read.csv("https://ericwfox.github.io/data/UN11.csv")
library(ggplot2)
```

a. 
```{r}
ggplot(UN11, aes(x = ppgdp, y = fertility)) + geom_point()
```
We should consider a log transformation because of how heavily right skewed the plot is. 

b. 
```{r}
ggplot(UN11, aes(x = log(ppgdp), y = log(fertility))) + geom_point() + geom_smooth(method = "lm", se = FALSE)
```
In my opinion the association appears to be reasonably linear. 

c. 
```{r}
lm1 = lm(log(fertility)~log(ppgdp), data = UN11)
summary(lm1)
```

d. $log(\hat{y}) = -.2log(\hat{x}) +2.66$

e. An increase in gross national product per person in US dollars can be associated with a decrease of fertility rate by .2. 

f. 
```{r}
new_x = data.frame(ppgdp = 1000)
predict(lm1, newdata = new_x, interval="prediction")
exp(1.234567)
exp(0.6258792)
exp(1.843256)

```
g. 
```{r}
par(mar=c(4,4,1,1), mfrow=c(1,2))
plot(predict(lm1), resid(lm1), xlab="Fitted values", ylab="Residuals")
abline(h=0)
hist(resid(lm1), main="", xlab="Residuals")

```

The residuals have a normal distribution and the variance looks constant. 

h.
```{r}
ind <- which(abs(rstandard(lm1)) > 2)
UN11[ind, ]

```
I don't think they need to be removed because it is already linear. 
