---
title: "HW3_632"
author: "Prashan A. Welipitiya"
date: "3/3/2020"
output: pdf_document
---

# Exercise 1

```{r}
library(ISLR)
#help(Auto)
library(ggplot2)
```
## a. 
```{r}
ggplot(data=Auto, aes(x = horsepower, y = mpg)) + geom_point()
```

## b. 
```{r}
lm1 = lm(mpg~horsepower + I(horsepower^2), data = Auto)
summary(lm1)
```
$$Y = 56.9 - 0.4x + 0.0012x^2$$

## c. 
```{r}
x_new = data.frame(horsepower = 150)
predict(lm1, newdata = x_new, interval = "prediction")
```
## d. 
```{r}
ggplot(data=Auto, aes(x = horsepower, y = mpg)) + geom_point() + stat_smooth(method = 'lm', formula = y ~ poly(x,2), se = FALSE)
```

## e. 

```{r}
par(mfrow = c(1, 2))
plot(lm1, 1:2)
```
There is fanning and non constant variance and the residuals deviate from the normal distribution. 

# Exercise 2

```{r}
#help(Carseats)
```

## a. 
```{r}
lm2 = lm(Sales~Price + Urban + US, data = Carseats)
summary(lm2)
```
## b.

A decrease in price by 0.05 is associated with an increase of a sale of one thousand units, when all other predictors are held firm.
A location in an urban area on average will sell 20 less units compared to a non urban area. 
A location in the US on average will sell 1,200 units more than a store outside the US. 

## c. 
$$\hat{y} = 13.04 - 0.05x_1 - 0.02x_2 + 1.2x_3$$
## d. 
The Urban variable. 

## e. 
```{r}
lm3 = lm(Sales~Price + US, data = Carseats)
summary(lm3)
```

## f. 
23.35% of the variation in sales can be explained by the regression moddel. 

## g. 
```{r}
confint(lm3)
```

